Flowchart of Current Algorithm

### 2008-10-27 docs/flowchart/flowchart.tex
found typo

\item {\bf Advect Base Enthalpy}$[(\rho h)_0^\inp,w_0^\inp,\psi^\inp] \rightarrow [(\rho h)_0]^\outp$\\
is the process by which we update the base state enthalpy through $\dt$ in time.
\begin{description}

>>>>

\item {\bf Advect Base Enthalpy}$[(\rho h)_0^\inp,w_0^\inp,\psi^\inp] \rightarrow [(\rho h)_0^\outp]$\\
is the process by which we update the base state enthalpy through $\dt$ in time.
\begin{description}
